Realizing temporal graphs from fastest travel times

### 2023-05-01 Arxiv-1-5-23/ARXIV_realizing-temporal_1-5-23.tex
Arxiv submission 1st of May

\usepackage{graphicx}
\graphicspath{{Figures/}}

@@

\bibliography{bibliography}

\clearpage

\appendix

>>>>

\usepackage{graphicx}
%%%%\graphicspath{{../Figures/}}

@@

\begin{thebibliography}{10}

	\bibitem{akrida2017complexity}
	Eleni~C Akrida, Leszek G{\k{a}}sieniec, George~B. Mertzios, and Paul~G
	Spirakis.
	\newblock The complexity of optimal design of temporally connected graphs.
	\newblock {\em Theory of Computing Systems}, 61:907--944, 2017.

	\bibitem{Akrida-explorer-21}
	Eleni~C. Akrida, George~B. Mertzios, Paul~G. Spirakis, and Christoforos
	Raptopoulos.
	\newblock The temporal explorer who returns to the base.
	\newblock {\em Journal of Computer and System Sciences}, 120:179--193, 2021.

	\bibitem{Arrighi2023Multi}
	Emmanuel Arrighi, Niels Gr{\"u}ttemeier, Nils Morawietz, Frank Sommer, and
	Petra Wolf.
	\newblock Multi-parameter analysis of finding minors and subgraphs
	in edge-periodic temporal graphs.
	\newblock In {\em Proceedings of the 48th International Conference on Current
		Trends in Theory and Practice of Computer Science (SOFSEM)}, pages 283--297,
	2023.

	\bibitem{augustine2022distributed}
	John Augustine, Keerti Choudhary, Avi Cohen, David Peleg, Sumathi
	Sivasubramaniam, and Suman Sourav.
	\newblock Distributed graph realizations.
	\newblock {\em IEEE Transactions on Parallel and Distributed Systems},
	33(6):1321--1337, 2022.

	\bibitem{barNoy2020efficiently}
	Amotz Bar{-}Noy, Keerti Choudhary, David Peleg, and Dror Rawitz.
	\newblock Efficiently realizing interval sequences.
	\newblock {\em SIAM Journal on Discrete Mathematics}, 34(4):2318--2337, 2020.

	\bibitem{Bar-NoyCPR20}
	Amotz Bar{-}Noy, Keerti Choudhary, David Peleg, and Dror Rawitz.
	\newblock Graph realizations: Maximum degree in vertex neighborhoods.
	\newblock In {\em Proceedings of the 17th Scandinavian Symposium and Workshops
		on Algorithm Theory (SWAT)}, pages 10:1--10:17, 2020.

	\bibitem{barNoy2021composed}
	Amotz Bar{-}Noy, David Peleg, Mor Perry, and Dror Rawitz.
	\newblock Composed degree-distance realizations of graphs.
	\newblock In {\em Proceedings of the 32nd International Workshop on
		Combinatorial Algorithms ({IWOCA})}, pages 63--77, 2021.

	\bibitem{barNoy2022GraphRealization}
	Amotz Bar-Noy, David Peleg, Mor Perry, and Dror Rawitz.
	\newblock Graph realization of distance sets.
	\newblock In {\em Proceedings of the 47th International Symposium on
		Mathematical Foundations of Computer Science (MFCS)}, pages 13:1--13:14,
	2022.

	\bibitem{behzad1976eccentric}
	Mehdi Behzad and James~E Simpson.
	\newblock Eccentric sequences and eccentric sets in graphs.
	\newblock {\em Discrete Mathematics}, 16(3):187--193, 1976.

	\bibitem{bixby1988almost}
	Robert~E Bixby and Donald~K Wagner.
	\newblock An almost linear-time algorithm for graph realization.
	\newblock {\em Mathematics of Operations Research}, 13(1):99--123, 1988.

	\bibitem{xuan_computing_2003}
	Binh-Minh Bui-Xuan, Afonso Ferreira, and Aubin Jarry.
	\newblock Computing shortest, fastest, and foremost journeys in dynamic
	networks.
	\newblock {\em International Journal of Foundations of Computer Science},
	14(02):267--285, 2003.

	\bibitem{CasteigtsCS22}
	Arnaud Casteigts, Timoth{\'{e}}e Corsini, and Writika Sarkar.
	\newblock Invited paper: Simple, strict, proper, happy: A study of reachability
	in temporal graphs.
	\newblock In {\em Proceedings of the 24th International Symposium on
		Stabilization, Safety, and Security of Distributed Systems ({SSS})}, pages
	3--18, 2022.

	\bibitem{casteigts2012time}
	Arnaud Casteigts, Paola Flocchini, Walter Quattrociocchi, and Nicola Santoro.
	\newblock Time-varying graphs and dynamic networks.
	\newblock {\em International Journal of Parallel, Emergent and Distributed
		Systems}, 27(5):387--408, 2012.

	\bibitem{casteigts2021finding}
	Arnaud Casteigts, Anne-Sophie Himmel, Hendrik Molter, and Philipp Zschoche.
	\newblock Finding temporal paths under waiting time constraints.
	\newblock {\em Algorithmica}, 83(9):2754--2802, 2021.

	\bibitem{chen1966realization}
	Wai-Kai Chen.
	\newblock On the realization of a $(p, s)$-digraph with prescribed degrees.
	\newblock {\em Journal of the Franklin Institute}, 281(5):406--422, 1966.

	\bibitem{chung2001distance}
	Fan Chung, Mark Garrett, Ronald Graham, and David Shallcross.
	\newblock Distance realization problems with applications to internet
	tomography.
	\newblock {\em Journal of Computer and System Sciences}, 63(3):432--448, 2001.

	\bibitem{culberson1989fast}
	Joseph~C. Culberson and Piotr Rudnicki.
	\newblock A fast algorithm for constructing trees from distance matrices.
	\newblock {\em Information Processing Letters}, 30(4):215--220, 1989.

	\bibitem{deligkas2022optimizing}
	Argyrios Deligkas and Igor Potapov.
	\newblock Optimizing reachability sets in temporal graphs by delaying.
	\newblock {\em Information and Computation}, 285:104890, 2022.

	\bibitem{enright2021deleting}
	Jessica Enright, Kitty Meeks, George~B. Mertzios, and Viktor Zamaraev.
	\newblock Deleting edges to restrict the size of an epidemic in temporal
	networks.
	\newblock {\em Journal of Computer and System Sciences}, 119:60--77, 2021.

	\bibitem{enright2021assigning}
	Jessica Enright, Kitty Meeks, and Fiona Skerman.
	\newblock Assigning times to minimise reachability in temporal graphs.
	\newblock {\em Journal of Computer and System Sciences}, 115:169--186, 2021.

	\bibitem{EMM22}
	Jessica~A. Enright, Kitty Meeks, and Hendrik Molter.
	\newblock Counting temporal paths.
	\newblock {\em CoRR}, abs/2202.12055, 2022.
	\newblock URL: \url{https://arxiv.org/abs/2202.12055}.

	\bibitem{erdos1960graphs}
	Paul Erd{\"o}s and Tibor Gallai.
	\newblock Graphs with prescribed degrees of vertices.
	\newblock {\em Mat. Lapok}, 11:264--274, 1960.

	\bibitem{erlebach2021temporal}
	Thomas Erlebach, Michael Hoffmann, and Frank Kammer.
	\newblock On temporal graph exploration.
	\newblock {\em Journal of Computer and System Sciences}, 119:1--18, 2021.

	\bibitem{ErlebachS20}
	Thomas Erlebach and Jakob~T. Spooner.
	\newblock A game of cops and robbers on graphs with periodic edge-connectivity.
	\newblock In {\em Proceedings of the 46th International Conference on Current
		Trends in Theory and Practice of Informatics (SOFSEM)}, pages 64--75, 2020.

	\bibitem{fellows2009multipleinterval}
	Michael~R. Fellows, Danny Hermelin, Frances Rosamond, and St{\'e}phane
	Vialette.
	\newblock On the parameterized complexity of multiple-interval graph problems.
	\newblock {\em Theoretical Computer Science}, 410(1):53--61, 2009.

	\bibitem{FJR13}
	Michael~R. Fellows, Bart M.~P. Jansen, and Frances~A. Rosamond.
	\newblock Towards fully multivariate algorithmics: {P}arameter ecology and the
	deconstruction of computational complexity.
	\newblock {\em European Journal of Combinatorics}, 34(3):541--566, 2013.

	\bibitem{Flu+19a}
	Till Fluschnik, Hendrik Molter, Rolf Niedermeier, Malte Renken, and Philipp
	Zschoche.
	\newblock Temporal graph classes: A view through temporal separators.
	\newblock {\em Theoretical Computer Science}, 806:197--218, 2020.

	\bibitem{frank1992augmenting}
	Andr{\'a}s Frank.
	\newblock Augmenting graphs to meet edge-connectivity requirements.
	\newblock {\em SIAM Journal on Discrete Mathematics}, 5(1):25--53, 1992.

	\bibitem{frank1994connectivity}
	Andr{\'a}s Frank.
	\newblock Connectivity augmentation problems in network design.
	\newblock {\em Mathematical Programming: State of the Art 1994}, 1994.

	\bibitem{frank1970connectivity}
	H.~Frank and Wushow Chou.
	\newblock Connectivity considerations in the design of survivable networks.
	\newblock {\em IEEE Transactions on Circuit Theory}, 17(4):486--490, 1970.

	\bibitem{FMNR22a}
	Eugen F\"uchsle, Hendrik Molter, Rolf Niedermeier, and Malte Renken.
	\newblock Delay-robust routes in temporal graphs.
	\newblock In {\em Proceedings of the 39th International Symposium on
		Theoretical Aspects of Computer Science (STACS)}, pages 30:1--30:15, 2022.

	\bibitem{FuchsleMNR22}
	Eugen F{\"{u}}chsle, Hendrik Molter, Rolf Niedermeier, and Malte Renken.
	\newblock Temporal connectivity: Coping with foreseen and unforeseen delays.
	\newblock In {\em Proceedings of the 1st Symposium on Algorithmic Foundations
		of Dynamic Networks ({SAND})}, pages 17:1--17:17, 2022.

	\bibitem{fulkerson1960zero}
	D.R. Fulkerson.
	\newblock Zero-one matrices with zero trace.
	\newblock {\em Pacific Journal of Mathematics}, 10(3):831--836, 1960.

	\bibitem{GolovachM17}
	Petr~A. Golovach and George~B. Mertzios.
	\newblock Graph editing to a given degree sequence.
	\newblock {\em Theoretical Computer Science}, 665:1--12, 2017.

	\bibitem{GolumbicTrenk04}
	Martin~Charles Golumbic and Ann~N. Trenk.
	\newblock {\em Tolerance Graphs}.
	\newblock Cambridge Studies in Advanced Mathematics. Cambridge University
	Press, 2004.

	\bibitem{gomory1961multi}
	Ralph~E Gomory and Tien~Chung Hu.
	\newblock Multi-terminal network flows.
	\newblock {\em Journal of the Society for Industrial and Applied Mathematics},
	9(4):551--570, 1961.

	\bibitem{grotschel1995design}
	Martin Gr{\"o}tschel, Clyde~L Monma, and Mechthild Stoer.
	\newblock Design of survivable networks.
	\newblock {\em Handbooks in Operations Research and Management Science},
	7:617--672, 1995.

	\bibitem{GHN04}
	Jiong Guo, Falk H{\"u}ffner, and Rolf Niedermeier.
	\newblock A structural view on parameterizing problems: Distance from
	triviality.
	\newblock In {\em Proceedings of the 1st International Workshop on
		Parameterized and Exact Computation (IWPEC)}, pages 162--173, 2004.

	\bibitem{hakimi1962realizability}
	S.~Louis Hakimi.
	\newblock On realizability of a set of integers as degrees of the vertices of a
	linear graph.~{I}.
	\newblock {\em Journal of the Society for Industrial and Applied Mathematics},
	10(3):496--506, 1962.

	\bibitem{hakimi1965distance}
	S.~Louis Hakimi and Stephen~S. Yau.
	\newblock Distance matrix of a graph and its realizability.
	\newblock {\em Quarterly of applied mathematics}, 22(4):305--317, 1965.

	\bibitem{hell2009linear}
	Pavol Hell and David Kirkpatrick.
	\newblock Linear-time certifying algorithms for near-graphical sequences.
	\newblock {\em Discrete Mathematics}, 309(18):5703--5713, 2009.

	\bibitem{KKK00}
	David Kempe, Jon~M. Kleinberg, and Amit Kumar.
	\newblock Connectivity and inference problems for temporal networks.
	\newblock {\em Journal of Computer and System Sciences}, 64(4):820--842, 2002.

	\bibitem{klobas2023interference}
	Nina Klobas, George~B. Mertzios, Hendrik Molter, Rolf Niedermeier, and Philipp
	Zschoche.
	\newblock Interference-free walks in time: Temporally disjoint paths.
	\newblock {\em Autonomous Agents and Multi-Agent Systems}, 37(1):1, 2023.

	\bibitem{KlobasMMS22}
	Nina Klobas, George~B. Mertzios, Hendrik Molter, and Paul~G. Spirakis.
	\newblock The complexity of computing optimum labelings for temporal
	connectivity.
	\newblock In {\em Proceedings of the 47th International Symposium on
		Mathematical Foundations of Computer Science (MFCS)}, pages 62:1--62:15,
	2022.

	\bibitem{Kuhn2011Dynamic}
	Fabian Kuhn and Rotem Oshman.
	\newblock Dynamic networks: Models and algorithms.
	\newblock {\em SIGACT News}, 42(1):82–96, mar 2011.

	\bibitem{Lenstra1983Integer}
	Hendrik~W. Lenstra.
	\newblock Integer programming with a fixed number of variables.
	\newblock {\em Mathematics of Operations Research}, 8:538--548, 1983.

	\bibitem{snapnets}
	Jure Leskovec and Andrej Krevl.
	\newblock {SNAP Datasets}: {Stanford} large network dataset collection.
	\newblock \url{http://snap.stanford.edu/data}, June 2014.

	\bibitem{lesniak1975eccentric}
	Linda Lesniak.
	\newblock Eccentric sequences in graphs.
	\newblock {\em Periodica Mathematica Hungarica}, 6:287--293, 1975.

	\bibitem{McConnellS02}
	Ross~M. McConnell and Jeremy~P. Spinrad.
	\newblock Construction of probe interval models.
	\newblock In {\em Proceedings of the 13th Annual {ACM-SIAM} Symposium on
		Discrete Algorithms (SODA)}, pages 866--875, 2002.

	\bibitem{McMorris98}
	F.R. McMorris, Chi Wang, and Peisen Zhang.
	\newblock On probe interval graphs.
	\newblock {\em Discrete Applied Mathematics}, 88(1):315--324, 1998.
	\newblock Computational Molecular Biology DAM - CMB Series.

	\bibitem{MertziosMS19}
	George~B. Mertzios, Othon Michail, and Paul~G. Spirakis.
	\newblock Temporal network optimization subject to connectivity constraints.
	\newblock {\em Algorithmica}, 81(4):1416--1449, 2019.

	\bibitem{Mertzios-transitivity21}
	George~B. Mertzios, Hendrik Molter, Malte Renken, Paul~G. Spirakis, and Philipp
	Zschoche.
	\newblock The complexity of transitively orienting temporal graphs.
	\newblock In {\em Proceedings of the 46th International Symposium on
		Mathematical Foundations of Computer Science (MFCS)}, pages 75:1--75:18,
	2021.

	\bibitem{MolterRZ21}
	Hendrik Molter, Malte Renken, and Philipp Zschoche.
	\newblock Temporal reachability minimization: Delaying vs. deleting.
	\newblock In {\em Proceedings of the 46th International Symposium on
		Mathematical Foundations of Computer Science (MFCS)}, pages 76:1--76:15,
	2021.

	\bibitem{morawietz2020timecop}
	Nils Morawietz, Carolin Rehs, and Mathias Weller.
	\newblock A timecop's work is harder than you think.
	\newblock In {\em Proceedings of the 45th International Symposium on
		Mathematical Foundations of Computer Science (MFCS)}, volume 170, pages
	71--1, 2020.

	\bibitem{morawietz2021timecop}
	Nils Morawietz and Petra Wolf.
	\newblock A timecop’s chase around the table.
	\newblock In {\em Proceedings of the 46th International Symposium on
		Mathematical Foundations of Computer Science (MFCS)}, 2021.

	\bibitem{Patrinos-Hakimi-72}
	A.N. Patrinos and S.~Louis Hakimi.
	\newblock The distance matrix of a graph and its tree realization.
	\newblock {\em Quarterly of Applied Mathematics}, 30:255--269, 1972.

	\bibitem{Rubei16}
	Elena Rubei.
	\newblock Weighted graphs with distances in given ranges.
	\newblock {\em Journal of Classification}, 33:282–--297, 2016.

	\bibitem{sapiezynski2015tracking}
	Piotr Sapiezynski, Arkadiusz Stopczynski, Radu Gatej, and Sune Lehmann.
	\newblock Tracking human mobility using wifi signals.
	\newblock {\em PloS one}, 10(7):e0130824, 2015.

	\bibitem{Schaefer1978complexity}
	Thomas~J. Schaefer.
	\newblock The complexity of satisfiability problems.
	\newblock In {\em Proceedings of the 10th Annual {ACM} Symposium on Theory of
		Computing (STOC)}, pages 216--226, 1978.

	\bibitem{Tamura93}
	H.~Tamura, M.~Sengoku, S.~Shinoda, and T.~Abe.
	\newblock Realization of a network from the upper and lower bounds of the
	distances (or capacities) between vertices.
	\newblock In {\em Proceedings of the 1993 IEEE International Symposium on
		Circuits and Systems (ISCAS)}, pages 2545–--2548, 1993.

	\bibitem{Wu2016Efficient}
	Huanhuan Wu, James Cheng, Yiping Ke, Silu Huang, Yuzhen Huang, and Hejun Wu.
	\newblock Efficient algorithms for temporal path computation.
	\newblock {\em {IEEE} Transactions on Knowledge and Data Engineering},
	28(11):2927--2942, 2016.

	\bibitem{Zsc+19}
	Philipp Zschoche, Till Fluschnik, Hendrik Molter, and Rolf Niedermeier.
	\newblock The complexity of finding separators in temporal graphs.
	\newblock {\em Journal of Computer and System Sciences}, 107:72--92, 2020.

\end{thebibliography}

### 2023-05-01 Figures/fig-W1-reduction.tex
Arxiv submission 1st of May

		\draw[rounded corners, dashed, gray] (-13, 5) rectangle (10, 1.5) {};
		\node (A) at (-10.5,4.5) {alignment gadget};

@@

		\draw[rounded corners, dashed, gray] (-9.5, 1) rectangle (1.5, -26) {};
		\node (A) at (-4,-25.5) {edge selection gadget for $i,j$};

		\draw[rounded corners, dashed, gray] (3.5, 1) rectangle (6.5, -26) {};
		\node[rotate=-90] (A) at (7,-23) {verification gadget for $j$};

@@

		\draw[edge, line width=1.5pt] (X1) --node[timelabel] {$t_1$} (VS);
		\draw[edge] (X2) --node[timelabel] {$t_2$} (VS);
		\draw[edge] (X3) --node[timelabel] {$t_3$} (VS);
		\draw[edge] (XM) --node[timelabel] {$t_m$} (VS);

		\draw[edge] (Y1) --node[timelabel,sloped] {$t_3+2$} (VS);
		\draw[edge] (Y2) --node[timelabel,sloped] {$t_m+2$} (VS);
		\draw[edge, line width=1.5pt] (Y3) --node[timelabel,sloped] {$t_1+2$} (VS);
		\draw[edge] (YM) --node[timelabel,sloped] {$t_2+2$} (VS);

		\draw[edge] (Y1) --node[timelabel] {$t_3+4$} (U11);
		\draw[edge] (Y2) --node[timelabel] {$t_m+4$} (U12);
		\draw[edge, line width=1.5pt] (Y3) --node[timelabel] {$t_1+4$} (U13);
		\draw[edge] (YM) --node[timelabel] {$t_2+4$} (U1M);

		\draw[edge] (U21) --node[timelabel] {$t_3+6$} (U11);
		\draw[edge] (U22) --node[timelabel] {$t_m+6$} (U12);
		\draw[edge, line width=1.5pt] (U23) --node[timelabel] {$t_1+6$} (U13);
		\draw[edge] (U2M) --node[timelabel] {$t_2+6$} (U1M);

		\draw[edge] (UN1) --node[timelabel,sloped] {$t_3+2n+4$} (UN11);
		\draw[edge] (UN2) --node[timelabel,sloped] {$t_m+2n+4$} (UN12);
		\draw[edge, line width=1.5pt] (UN3) --node[timelabel,sloped] {$t_1+2n+4$} (UN13);
		\draw[edge] (UNM) --node[timelabel,sloped] {$t_2+2n+4$} (UN1M);

		\draw[edge] (U2N1) --node[timelabel,sloped] {$t_3+8n+4$} (VSS);
		\draw[edge] (U2N2) --node[timelabel,sloped] {$t_m+8n+4$} (VSS);
		\draw[edge, line width=1.5pt] (U2N3) --node[timelabel,sloped] {$t_1+8n+4$} (VSS);
		\draw[edge] (U2NM) --node[timelabel,sloped] {$t_2+8n+4$} (VSS);

		\draw[edge] (VH11) --node[timelabel,sloped] {$n^9$} (VH12);
		\draw[edge] (VH12) --node[timelabel,sloped] {$n^9+2$} (VH111);
		\draw[edge] (VH12) --node[timelabel] {$n^9+1$} (VH13);
		\draw[edge] (VH13) --node[timelabel,sloped] {$n^9$} (VH14);
		\draw[edge] (VH13) --node[timelabel,sloped] {$n^9+2$} (VH144);

		\draw[edge] (VH21) --node[timelabel,sloped] {$n^9$} (VH22);
		\draw[edge] (VH22) --node[timelabel,sloped] {$n^9+2$} (VH211);
		\draw[edge] (VH22) --node[timelabel] {$n^9+1$} (VH23);
		\draw[edge] (VH23) --node[timelabel,sloped] {$n^9$} (VH24);
		\draw[edge] (VH23) --node[timelabel,sloped] {$n^9+2$} (VH244);

		\draw[edge] (VH31) --node[timelabel,sloped] {$n^9$} (VH32);
		\draw[edge] (VH32) --node[timelabel,sloped] {$n^9+2$} (VH311);
		\draw[edge] (VH32) --node[timelabel] {$n^9+1$} (VH33);
		\draw[edge] (VH33) --node[timelabel,sloped] {$n^9$} (VH34);	
		\draw[edge] (VH33) --node[timelabel,sloped] {$n^9+2$} (VH344);

		\draw[edge] (VH41) --node[timelabel,sloped] {$n^9$} (VH42);
		\draw[edge] (VH42) --node[timelabel,sloped] {$n^9+2$} (VH411);
		\draw[edge] (VH42) --node[timelabel] {$n^9+1$} (VH43);
		\draw[edge] (VH43) --node[timelabel,sloped] {$n^9$} (VH44);	
		\draw[edge] (VH43) --node[timelabel,sloped] {$n^9+2$} (VH444);

@@

		\draw[edge] (W) --node[timelabel] {$1$} (W1);
		\draw[edge] (W) --node[timelabel] {$1$} (W2);
		\draw[edge] (W) --node[timelabel] {$1$} (W3);
		\draw[edge] (W) --node[timelabel] {$1$} (W4);
		\draw[edge] (W) --node[timelabel] {$1$} (W5);
		\draw[edge] (W) --node[timelabel] {$1$} (W6);

		\draw[edge] (X1) --node[timelabel] {$t_1$} (W1);
		\draw[edge] (VH11) --node[timelabel] {$n^9$} (W2);
		\draw[edge] (VH21) edge[bend left=50] node[timelabel] {$n^9$} (W3);
		\draw[edge] (VH31) --node[timelabel] {$n^9$} (W4);
		\draw[edge] (YI) --node[timelabel] {$n^8-1$} (W5);
		\draw[edge] (VH41) edge[bend right=50] node[timelabel] {$n^9$} (W6);

		\draw[edge] (YI) --node[timelabel] {$n^8$} (VI0);

		\draw[edge] (VII1) --node[timelabel] {$t'$} (UI1);
		\draw[edge] (UI1) --node[timelabel] {$t'+2$} (UI2);
	\end{tikzpicture}

>>>>

	\draw[rounded corners, dashed, gray] (-13, 5.4) rectangle (10, 1.6) {};
	\node (A) at (-10.5,4.5) {alignment gadget};

@@

	\draw[rounded corners, dashed, gray] (-9.5, 1.4) rectangle (1.5, -26) {};
	\node (A) at (-4,-25.5) {edge selection gadget for $i,j$};

	\draw[rounded corners, dashed, gray] (3.5, 1.4) rectangle (6.5, -26) {};
	\node[rotate=-90] (A) at (7,-21.5) {verification gadget for $j$};

@@

	\draw[edge] (X1) --node[] {} (VS);
	\draw[edge] (X2) --node[] {} (VS);
	\draw[edge] (X3) --node[] {} (VS);
	\draw[edge] (XM) --node[] {} (VS);

	\draw[edge] (Y1) --node[] {} (VS);
	\draw[edge] (Y2) --node[] {} (VS);
	\draw[edge] (Y3) --node[] {} (VS);
	\draw[edge] (YM) --node[] {} (VS);

	\draw[edge] (Y1) --node[] {} (U11);
	\draw[edge] (Y2) --node[] {} (U12);
	\draw[edge] (Y3) --node[] {} (U13);
	\draw[edge] (YM) --node[] {} (U1M);

	\draw[edge] (U21) --node[] {} (U11);
	\draw[edge] (U22) --node[] {} (U12);
	\draw[edge] (U23) --node[] {} (U13);
	\draw[edge] (U2M) --node[] {} (U1M);

	\draw[edge] (UN1) --node[] {} (UN11);
	\draw[edge] (UN2) --node[] {} (UN12);
	\draw[edge] (UN3) --node[] {} (UN13);
	\draw[edge] (UNM) --node[] {} (UN1M);

	\draw[edge] (U2N1) --node[] {} (VSS);
	\draw[edge] (U2N2) --node[] {} (VSS);
	\draw[edge] (U2N3) --node[] {} (VSS);
	\draw[edge] (U2NM) --node[] {} (VSS);

	\draw[edge] (VH11) --node[] {} (VH12);
	\draw[edge] (VH12) --node[] {} (VH111);
	\draw[edge] (VH12) --node[] {} (VH13);
	\draw[edge] (VH13) --node[] {} (VH14);
	\draw[edge] (VH13) --node[] {} (VH144);

	\draw[edge] (VH21) --node[] {} (VH22);
	\draw[edge] (VH22) --node[] {} (VH211);
	\draw[edge] (VH22) --node[] {} (VH23);
	\draw[edge] (VH23) --node[] {} (VH24);
	\draw[edge] (VH23) --node[] {} (VH244);

	\draw[edge] (VH31) --node[] {} (VH32);
	\draw[edge] (VH32) --node[] {} (VH311);
	\draw[edge] (VH32) --node[] {} (VH33);
	\draw[edge] (VH33) --node[] {} (VH34);	
	\draw[edge] (VH33) --node[] {} (VH344);

	\draw[edge] (VH41) --node[] {} (VH42);
	\draw[edge] (VH42) --node[] {} (VH411);
	\draw[edge] (VH42) --node[] {} (VH43);
	\draw[edge] (VH43) --node[] {} (VH44);	
	\draw[edge] (VH43) --node[] {} (VH444);

@@

	\draw[edge] (W) --node[] {} (W1);
	\draw[edge] (W) --node[] {} (W2);
	\draw[edge] (W) --node[] {} (W3);
	\draw[edge] (W) --node[] {} (W4);
	\draw[edge] (W) --node[] {} (W5);
	\draw[edge] (W) --node[] {} (W6);

	\draw[edge] (X1) --node[] {} (W1);
	\draw[edge] (VH11) --node[] {} (W2);
	\draw[edge] (VH21) edge[bend left=50] node[] {} (W3);
	\draw[edge] (VH31) --node[] {} (W4);
	\draw[edge] (YI) --node[] {} (W5);
	\draw[edge] (VH41) edge[bend right=50] node[] {} (W6);

	\draw[edge] (YI) --node[] {} (VI0);

	\draw[edge] (VII1) --node[] {} (UI1);
	\draw[edge] (UI1) --node[] {} (UI2);
\end{tikzpicture}

### 2023-05-01 ICALP 2023/ICALP23-RealizingTemporalGraphs.tex
Arxiv submission 1st of May

\end{tikzpicture}
}
\caption{Illustration of the temporal graph $(G,\lambda)$ from the NP-hardness reduction, 
	where the NAE 3-SAT formula $\phi$ is of form $\phi = \text{NAE}(x_1, \overline{x}_2, x_3) \wedge \text{NAE}(\overline{x}_1, x_2, x_4)$.
To improve the readability, we draw edges between vertices $x_i^T$ and $x_j^F$ (where $i \neq j$) with gray dotted lines.
Presented is the labeling of $G$ corresponding to the assignment $x_1=x_2=\textsc{true}$ and $x_3,x_4=\textsc{false}$,
where all unlabeled edges get the label $2$.
}\label{fig:NP-example}
\end{figure}
%
We set $\Delta$ to some constant larger than two, that is, $\Delta\ge 3$. Next, we specify the durations in the matrix $D$ between all vertex pairs.
For the sake of simplicity we write $D_{u,v}$ as $d(u,v)$,
where $u,v$ are two vertices of $G$. 
We start by setting the value of $d(u,v) = 1$ where $u$ and $v$ are two adjacent vertices in $G$.
\begin{itemize}
    %\item For each variable $x$ in $\phi$ we specify the following distances between the non-adjacent variable vertices:
    %$d(x_1,x_2)=2$. 
    %\item For pair of variable $x,y$ in $\phi$ with $x\neq y$ we specify the following 
    %$d(x_1,y^T)=d(x_1,y^F)=3$, $d(x_2,y^T)=d(x_2,y^F)=2$.
    \item For each variable $x_i$ in $\phi$ and the super vertex $v$
    we specify the following durations:
    $d(x_i,v)=2$ and $d(v,x_i)= \Delta $. %, $d(x_2,v)=3$.
    \item For each clause $c$ in $\phi$ and the super vertex $v$
    we specify the following durations:
    $d(c,v)=2$ and $d(v,c)= \Delta - 1$.
    \item Let $x_i$ be a variable that appears in clause $c$, then  we specify the following durations:
    $d(c,x_i)=2$ and $d(x_i,c)=\Delta$.
    If $x_i$ appears non-negated in $c$ we specify the following durations:
    $d(c,x_i^F)=2$ and $d(x_i^F,c)=\Delta$.
    If $x_i$ appears negated in $c$ we specify the following duratios:
    $d(c,x_i^T)=2$ and $d(x_i^T,c)=\Delta$.
    \item Let $x_i$ be a variable that does \emph{not} appear in clause $c$, then we specify the following duratios:
    $d(x_i,c)=\Delta$, $d(c,x_i)=2\Delta + 2$
    and
    $d(c,x_i^T)=d(c,x_i^F)=2$, $d(x_i^T,c)=d(x_i^F,c)=\Delta$. 
    \item For each pair of variables $x_i \neq x_j$ in $\phi$ we specify the following duratios:
    $d(x_i,x_j)=2\Delta +1$ and
    $d(x_i,x_j^T)=d(x_i,x_j^F)=\Delta + 1$.
    \item For each pair of clauses $c_i \neq c_j$ in $\phi$ we specify the following duratios:
    $d(c_i,c_j)= \Delta + 1$.
\end{itemize}
This finishes the construction of the instance $(D,\Delta)$ of \deltaExact\, which can clearly be done in polynomial time. In the remainder we show that $(D,\Delta)$ is a \textsc{Yes}-instance of \deltaExact\ if and only if NAE 3-SAT formula $\phi$ is satisfiable.

>>>>

\end{tikzpicture}
}
\caption{Illustration of the temporal graph $(G,\lambda)$ from the NP-hardness reduction, 
	where the NAE 3-SAT formula $\phi$ is of form $\phi = \text{NAE}(x_1, \overline{x}_2, x_3) \wedge \text{NAE}(x_1, x_2, x_4)$.
	To improve the readability, we draw edges between vertices $x_i^T$ and $x_j^F$ (where $i \neq j$) with gray dotted lines.
	Presented is the labeling of $G$ corresponding to the assignment $x_1=x_2=\textsc{true}$ and $x_3,x_4=\textsc{false}$,
	where all unlabeled edges get the label $2$.
}\label{fig:NP-example}
\end{figure}
%
We set $\Delta$ to some constant larger than two, that is, $\Delta\ge 3$. Next, we specify the durations in the matrix $D$ between all vertex pairs.
For the sake of simplicity we write $D_{u,v}$ as $d(u,v)$,
where $u,v$ are two vertices of $G$. 
We start by setting the value of $d(u,v) = 1$ where $u$ and $v$ are two adjacent vertices in $G$.
\begin{itemize}
    %\item For each variable $x$ in $\phi$ we specify the following distances between the non-adjacent variable vertices:
    %$d(x_1,x_2)=2$. 
    %\item For pair of variable $x,y$ in $\phi$ with $x\neq y$ we specify the following 
    %$d(x_1,y^T)=d(x_1,y^F)=3$, $d(x_2,y^T)=d(x_2,y^F)=2$.
    \item For each variable $x_i$ in $\phi$ and the super vertex $v$
    we specify the following durations:
    $d(x_i,v)=2$ and $d(v,x_i)= \Delta $. %, $d(x_2,v)=3$.
    \item For each clause $c$ in $\phi$ and the super vertex $v$
    we specify the following durations:
    $d(c,v)=2$ and $d(v,c)= \Delta - 1$.
    \item Let $x_i$ be a variable that appears in clause $c$, then  we specify the following durations:
    $d(c,x_i)=2$ and $d(x_i,c)=\Delta$.
    If $x_i$ appears non-negated in $c$ we specify the following durations:
    $d(c,x_i^F)=2$ and $d(x_i^F,c)=\Delta$.
    If $x_i$ appears negated in $c$ we specify the following duratios:
    $d(c,x_i^T)=2$ and $d(x_i^T,c)=\Delta$.
    \item Let $x_i$ be a variable that does \emph{not} appear in clause $c$, then we specify the following duratios:
    $d(x_i,c)=\Delta$, $d(c,x_i)=2\Delta + 2$
    and
    $d(c,x_i^T)=d(c,x_i^F)=2$, $d(x_i^T,c)=d(x_i^F,c)=\Delta$. 
    \item For each pair of variables $x_i \neq x_j$ in $\phi$ we specify the following duratios:
    $d(x_i,x_j)=2\Delta +1$ and
    $d(x_i,x_j^T)=d(x_i,x_j^F)=\Delta + 1$.
    \item For each pair of clauses $c_i \neq c_j$ in $\phi$ we specify the following duratios:
    $d(c_i,c_j)= \Delta + 1$.
\end{itemize}
This finishes the construction of the instance $(D,\Delta)$ of \deltaExact\, which can clearly be done in polynomial time. In the remainder we show that $(D,\Delta)$ is a \textsc{Yes}-instance of \deltaExact\ if and only if NAE 3-SAT formula $\phi$ is satisfiable.
